Response to the defense feedback

### 2021-06-19 Chapter-3/Chapter-3.tex
Updates from Overleaf

\noindent where $PC$ represents the path condition. An adversary can observe which branch the code executes if the branch condition
equals $t_b$. We use the constraint $c_i : f_i(\beta, k, m) = t_b$ to model
the observation ($o$) on secret-dependent control-transfers. Note that in the
above definition, $m$ is also a variable. So it is possible for some $m \in M$,
we cannot find a pair of two different $k_{i1}$ and $k_{i2}$ satisfying the above inequation. For example, in Figure~\ref{fig:chapter3:cf}, if $m = \mathtt{0}$, the function \textsf{example1} will always execute the branch 2. However, if $m = \mathtt{0xffffffff}$ and $k = \mathtt{0}$, the function \textsf{example1} executes the branch 1 and the function \textsf{example1} executes the branch 2 when $k = \mathtt{0xf000000}$.

>>>>

\noindent where $PC$ represents the path condition. An adversary can observe which branch the code executes if the branch condition
equals $t_b$. We use the constraint $c_i : f_i(\beta, k, m) = t_b$ to model
the observation ($o$) on secret-dependent control-transfers. Note that in the
above definition, $m$ is also a variable. So it is possible for some $m \in M$,
we cannot find a pair of two different $k_{i1}$ and $k_{i2}$ satisfying the above inequation. For example, in Figure~\ref{fig:chapter3:cf}, if $m = \mathtt{0}$, the function \textsf{example1} will always execute the branch 2. However, if $m = \mathtt{0xffffffff}$, the function \textsf{example1} executes the branch 1 when $k = \mathtt{0}$, and the function \textsf{example1} executes the branch 2 when $k = \mathtt{0xf000000}$.
